### 2012-10-09 intention motor representation joint action (paper 3)/conf budapest philosophy 2012-11/shared agency and motor representation.tex
shared agency version for budapest

\def \ititle {Motor Representation \\ and Shared Intention}
\def \isubtitle {}
\def \iauthor {
\textit{Collective Intentionality}, Manchester, August 2012}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
%\author{}
%\date{}

@@

\begin{abstract}
\noindent
On the assumption that motor representation plays a role in explaining how effective joint action is possible, do we also need motor representation to explain what joint action is? Philosophers tend to assume that motor representation is only an enabling condition for joint action and of no direct interest to narrowly philosophical theories of joint action and shared intention. In this talk I shall argue that social motor representation and shared intention have distinctive roles in explaining the purposiveness of joint action. This gives rise to a challenge. On the one hand, effective joint action—imagine two people erecting a tent in a gale together—sometimes requires both shared intentions and social motor representations plus a certain kind of harmony between the two. On the other hand, recognizing their distinctive roles precludes the existence of direct inferential links between shared intentions and social motor representations. The challenge is to explain how these two kinds of representation could sometimes harmoniously contribute to effective joint action despite the lack of inferential integration. 
\end{abstract}

\section{Introduction}
Which events are joint actions?
Most philosophers and many (but not all) psychologists appear to assume that this question can be fully answered just in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared (or `collective') intention.
On this widely held view, for an event to be a joint action is for it to be appropriately related to a shared intention.

[\textit{Short version: One consideration in favour of this view is ... and jump to the second consideration towards the end of  section \ref{text:second_consideration} on page \vpageref{text:second_consideration}.}]

\subsection{What is shared intention?}
Of course this answer to the question about which events are joint actions assumes that we know what shared or collective intention is.
But there are many accounts of it.
Still, I think most people would agree that shared intention stands to joint action approximately as plain vanilla intention stands to ordinary, individual action
Further,
on all or most leading accounts of shared intention, each of the following is a necessary condition:

\begin{description}

\item[awareness of joint-ness] Agents acting on a shared intention know that they are not acting individually; they have `a conception of themselves as contributors to a collective end.'\footnote{
	\citet[p.\ 10]{Kutz:2000si}.  Compare \citet[p.\ 361]{Roth:2004ki}: `each participant ... can answer the question of what he is doing or will be doing by saying for example ``We are walking together'' or ``We will/intend to walk together.''' 
Relatedly, \citet[p. 56]{miller_social_2001} requires that each agent believes her actions are interdependent with the other agent's.
}

\item[awareness of others' agency]  When agents act on a shared intention, each is aware of at least one of the others as an intentional agent.\footnote{
	Compare \citet[p.\ 333]{Bratman:1992mi}: `Cooperation ... is cooperation between intentional agents each of whom sees and treats the other as such'.  See also \citet[p.\ 105]{Searle:1990em}: `The biologically primitive sense of the other person as a candidate for shared intentionality is a necessary condition of all collective behavior' 
}

\item[awareness of others' states or commitments] When two agents share an intention that they F, each is aware of, or has individuating beliefs about, some of the other's intentions, beliefs or commitments concerning F.\footnote{
This condition is necessary for shared intention even on what \citet[p.\ 40]{tuomela_collective_2000} calls `the weakest kind of collective intention'.  But it may not be necessary if, as \citet{Gold:2007zd} suggest, shared intentions are constitutively intentions formed by a certain kind of reasoning.
% "if the distinctive feature of collective intentions is to be found in the reasoning by which they were formed, then an analysis that focuses on the intentions themselves will miss the feature that makes collective intentions collective. " 
}

\end{description}
%
I think we can go even further and say that, 
on most accounts,
where joint action involves shared intention, the agents act in part \emph{because} of their awareness of joint-ness, of others' agency and of others' states or commitments.

What follows assumes that where one or more of these three conditions is not met, there is no shared intention.

\subsection{Why shared intention?}
Why might anyone hold that for an event to be a joint action is for it to be appropriately related to a shared intention?
Two considerations favour this view.

First, the view might be motivated by appeal to some well-known contrast cases.
Contrast cases are pairs of events which are similar in terms of the behaviour and coordination they involve but where one is a joint action while the other is not.  
Thus \citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together is a joint action whereas merely walking side by side is not. 
Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first is a case of joint action, the second is not; but the same movements occur in both.  
These sorts of contrast case invite the question, 
How do joint actions differ from individual but parallel actions? 
Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
And Searle’s example shows that the difference between joint action and parallel individual action can’t just be that the actions have a common effect because merely parallel actions can have common effects too. 
If someone thought that it is possible to distinguish systematically between the contrast cases by appeal to shared intention (and perhaps only by appeal to shared intention), this could motivate holding that for an event to be a joint action is for it to be appropriately related to a shared intention.

@@

\subsection{My view}
On the second consideration, 
we take for granted that there is a parallel between joint action and ordinary, individual action.
But is the standard view about the relation between action and intention correct?

Not everyone accepts the standard view.
Some philosophers allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Michael Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' \citet[p.\ 251]{bratman:2000_valuing}.%
%\footnote{
%For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
%describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
%}

Others reject the standard view without asserting there can be action without intention.
Instead they claim that ingredients other than intention are needed to say which events are actions.
In particular, some claim that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{pacherie:2000_content,butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.

Our aim in this talk is to defend a parallel view about joint action. 
%(Parallel to the latter view, that is: not saying that creatures without any shared intentions are capable of joint actions.)
We shall consider the possibility that fully explaining which events are joint actions requires appeal to structures of motor representation and not only to shared intention.
%***what's the argument for this second claim!?

Please bear in mind that we are not trying to get rid of, or replace, the notion of shared intention.
%I take for granted that a notion of shared intention is needed for explaining which events are joint actions. 
%My concern is only with the possibility that additional ingredients are needed as well.
In fact recognising that motor representation is needed to say which events are joint actions may make it easier to understand what shared intention is.

\section{Intention and Motor Representation}
[\emph{*Probably skip all of this section in the talk}]

So that you can see where this is going, let me briefly explain what stands behind the view that motor representation is needed in addition to intention in saying which events are actions.

A basic question about ordinary, individual action is:
What is the relation between a purposive action and the outcome or outcomes to which it is directed?
Purposive actions typically have many actual outcomes.
Grabbing little Isabel by the hands I swing her around, causing her to laugh and, simultaneously, breaking a vase.
Either or both of these might be outcomes to which my action is directed.
Note also that some or all of the outcomes to which my action was directed might not be among its actual outcomes; after all, actions can fail.
So among all the actual and possible outcomes of my action, one or some are singled out as specially related to this action.
The question is what singles out the outcome or outcomes, actual or merely possible, to which a particular purposive is directed.

This question is closely related to a second.
Ordinary purposive actions are sometimes composed of more than one motor action.  My swinging Isabel around includes my reaching for her wrists, grasping them and then spinning us around.  
But  my action doesn’t include other things which I might be doing simultaneously, like refusing a cup of tea with my eyes or  trying to determine whether that smell is coming from Isabel’s sister Hannah’s nappy.
The second question, then, is this: For a particular action directed to a specified goal, what determines which activities%
\footnote{
As we use the term `activities',
all actions are activities 
and so are  things like reaching and grasping.
This should make it clear that our position does not depend on whether or not reachings and the like are  actions.
} 
comprise the purposive action and which do not?

The standard answer to both questions involves intention.
An intention represents an outcome, coordinates the one or several activities which comprise the action, and coordinates these activities in a way that would normally facilitate the outcome's occurrence.
What binds component activities together into larger purposive actions?  
It is the fact that these actions are all consequences of plans involving a single intention (and are all appropriately related to those plans).
What singles out an actual or possible outcome as one to which the component activities are collectively directed?  
It is the fact that this outcome is represented by the intention.
So the intention is what binds component actions together into purposive actions and links the action taken as a whole to the outcomes to which they are directed.

Motor representations are relevantly similar to intentions,
as some have recently argued (\citealp[pp.\ 189-90]{pacherie:2008_action}; \citealp{butterfill:2012_intention}).
Of course motor representations differ from intentions in some important ways (as these authors note).
But they are similar in the respects that matter for explaining the purposiveness of action.
For, like intentions, some motor representations represent outcomes and not merely kinematic features of action.
Like intentions, some motor representations play a role in coordinating multiple  component activities by virtue of their role as elements in hierarchically structured plans.
And, like intentions, some motor representations coordinate these activities in a way that would normally facilitate the outcome’s occurrence.
So anyone who accepts the standard story about purposive action and intention
should also accept that a similar story about purposive action and motor representation.
Given that the two basic questions about ordinary, individual purposive action can also be answered by appeal to intention,
they can also be answering by appeal to motor representation.
This motivates the following view.
Not all purposive actions are bound together and linked to outcomes by intentions. 
In some cases what binds together purposive actions and links them to outcomes are motor representations.
%In some cases, the purposiveness of an action is grounded in a motor representation of an outcome; in other cases it is grounded in an intention.
And of course in many cases it may be that both intention and motor representation are involved.

This is one reason for supposing that motor representation is not merely an enabling condition for ordinary, individual action but also plays a role in explaining what action is (just as intention does).
Now let’s return to joint action.

\section{Social motor representation}
We start from the premise that some joint actions are facilitated by reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent.

This needs unpacking. 
A \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.
We follow several psychologists and philosophers in supposing that motor representations feature in planning and monitoring action \citep[e.g.]{wolpert:1995internal, miall:1996_forward}.
One consequence is that motor representations are not concerned with merely kinematic or dynamic features of actions only.
Rather, some motor representations represent outcomes, such as the movement of a target object from one place to another.

@@

Two or more agents have \emph{reciprocal} motor representations  just if there is a single outcome and each agent has a motor representation of that outcome. 
It is hardly controversial that reciprocal motor representations exist, for their existence is suggested by by a large body of research on motor cognition in action observation.
What is much more controversial is that reciprocal motor representation occurs in joint action.
Some of the research that Gunether Knoblich presented supports the claim that there are reciprocal motor representations in joint action, and he suggests that these enable joint action.%
\footnote{
See \citet{kourtis:2012_predictive}: `the partner’s expected action is simulated at the motor level, which probably facilitates effective performance of the joint action.'
\citet{kourtis:2010_favoritism} show that 
reciprocal motor representation is more likely to occur in joint action than is mere observation. 
See also \citet{Knoblich:2003nf}.
 }

I want to go a tiny step further and suggest that in joint action there are sometimes reciprocal, agent-neutral representations of outcomes whose obtaining would normally involve action on the part of all of the agents.
So when we act together, some of my motor representations may concern outcomes that are partly but not entirely to be realised by my actions.
For example, suppose our task is to move an object from A to B, where you pick it up and pass it to me so that I can then place it.
In this case I may represent the movement of the object from A to B and not only the component movements.
I represent a collective outcome of our actions and not just outcomes to which each of our actions are individually directed.
%
%So it is not just that, when we act together, I represent the outcomes to which your actions are directed and the outcomes to which my actions are directed; I may also represent an outcome to which all of our actions are directed.

We shall use the term \emph{social} motor representation as an abbreviation for the reciprocal, agent-neutral motor representation of outcomes whose obtaining would normally require action on the part of each reciprocating agent.
(Of course we cannot assume in advance of argument that such reciprocal, agent-neutral motor representations are social in any interesting sense;
but we are using the term `social' in a non-standard way as an abbreviation, one that reflects our aim.)

What follows is speculative philosophy: we take for granted that sometimes social motor representation facilitates joint action and ask whether this conjecture bears on our question about which events are joint actions.

@@

To answer this question
let us take a step back and consider an individual action.
Suppose an agent moves a mug from one place to another, passing it from her left hand to her right hand half way.
It is a familiar idea that motor planning, like planning generally, involves starting with relatively abstract representations of outcomes and gradually filling in details.
We can capture this by supposing that 
motor representations for planning and monitoring action involve a hierarchical structure of representations.
At the top we might find a relatively abstract representation of an outcome, in this case of the movement of the object from one location to another.
Action-relevant details are progressively filled in by representations at lower stages of the hierarchy. 
Now in the action we are considering there is a need, even for the single agent, to coordinate the exchange between the two hands.
How is this achieved? 
We suppose that part of the answer involves the fact that planning for the movements of each hand is not done entirely independently.
Rather there is a plan for the whole action
and plans for the movements of each hand are components of this larger plan.
It is in part because they are parts of a larger plan that the plan for one hand constrains and is constrained by the plan for the other hand.

How is this relevant to the case of joint action?
In joint action the agents have the same goal, to move the object from one place to another.
They also face a similar coordination problem, requiring a precisely timed swap from one hand to another.
Now suppose, 
inspired by Koutis et al’s and others' findings,
that the same planning is involved in the individual case (where one agent performs the whole action) and in the joint action case (where the action is distributed between two agents).
The planning is the same almost up to the actual muscle contractions.

How could this be helpful?
Suppose the agents' planning processes are similar enough that, for a given context and problem, they will produce approximately the same plans.
Then having each agent plan the whole joint action means that (i) each agent plans the other agent's action,
(ii) each agent's plan for the other agent's action is approximately the same as that agent's plan for her own action,
and 
(iii) each  agent's plans for their own action are constrained by their plans for the other agent's action.

@@

\section{Grounding the purposiveness of joint action}
So far we have only been considering a possible role for social motor representation in facilitating joint action.  
Our primary concern, though, is with what joint action is.
The details of how 
social motor representation enables joint action
 already give us grounds for holding that motor representation has a role to play in explaining which events are joint actions.
To see why,
let’s go back to individual action for a moment again.

[***moved to earlier]

The same two questions we asked about ordinary, individual action also arise for joint action.
%What is the relation between a purposive joint action and the outcome or outcomes to which it is directed?
What singles out the outcome or outcomes to which a purposive joint action is directed?
And what binds together the various activities (of several agents) that make up the joint action?
%A difference in the case of joint action is, of course, that the component activities are not activities of a single agent.

If we appeal to a notion of shared intention,
we can answer these questions about joint action in a way that is superficially similar to way we answered the parallel questions about ordinary, individual action.
A shared intention is what relates purposive joint actions to the outcomes to which they are directed.
For the shared intention 
involves a representation, on the part of each agent, of an outcome,
coordinates the several agents’ activities
and 
coordinates the several agents’ activities in such a way that would normally facilitate the occurrence of the represented outcome.
This is how a shared intention can bind together the activities comprising a joint action and link them to an outcome.
%Shared intention does for joint action roughly what ordinary intention does for ordinary, individual action.

@@

What we are suggesting is very simple.
Given the correctness of a standard view about shared intention in joint action, 
and 
given that in ordinary, individual action, motor representations  bind together activities and link them to outcomes,
it is plausible that 
in joint action, several agents' activities can be bound together and linked to an outcome by social motor representation.
That is,
the purposiveness of a joint action can be grounded not only in shared intention, but also in social motor representation.

\section{Social motor representation: like shared intention}
It may be helpful to compare and contrast the notion of social motor representation with a notion of shared intention. 
We shall use Bratman's account of shared intention as it is the best developed. 
Here are Bratman’s collectively sufficient\footnotemark \ conditions for you and I to have a shared intention that we J:
%
\footnotetext{
In \citet{Bratman:1992mi}, the following were offered as jointly sufficient \textit{and individually necessary} conditions; the retreat to sufficient conditions occurs in \citet[][pp.\ 143-4]{Bratman:1999fr} where he notes that `for all that I have said, shared intention might be multiply realizable.'
} 
%
\begin{quote}
\label{quote:bratman_account}
`1. (a) I intend that we J and (b) you intend that we J

@@

If, as we have just argued, social motor representations play a role analogous to the structure of intentions and knowledge which Bratman identifies as sufficient for shared intention, then this is a  (non-decisive)  reason to think that motor representations can ground the purposiveness of a joint action.

>>>>

\def \ititle {Shared Agency and Motor Representation}
\def \isubtitle {}
\def \iauthor {CEU Philosophy, Budapest, 20 November 2012}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper3}
%\author{}
%\date{}

@@

\begin{abstract}
\noindent
Shared agency is paradigmatically involved when two or more people paint a house together, tidy the toys away together, or lift a two-handled basket together.  To characterise shared agency, some philosophers have appealed to a special kind of intention or structure of intention, knowledge or commitment often called `shared intention'.  In this paper we argue that fully characterising shared agency may additionally require appeal to  motor representation.  Shared agency is not only a matter of what we intend: sometimes it also depends on interlocking structures of motor representation.  This may have consequences for some metaphysical, normative and phenomenological questions about shared agency.

\end{abstract}

%\section{***EVIDENCE***}
%I now think three bits of evidence are relevant:
%\begin{enumerate}
%\item The GROOP effect shows that there are representations which specify each agent's task in relation to the other (so they are not simple representing the outcomes to which each of their actions are directed; they are representing an outcome to which their actions taken together are directed.)
%\item \citet{kourtis:2012_predictive} shows that motor planning can occur for others' actions when we are engaged in joint action with them.
%\item Vesper's ESPP paper (on jumping together and imagining jumping together --- jumping is published \citep{vesper:2012_jumping}, imagining jumping is about to be submitted (as of August 2012).  This shows that individuals are capable of running motor simulations of multiple roughly simultaneous actions.
%\end{enumerate}
%

\section{Introduction}
Shared agency is paradigmatically involved when two (or more) people 
	paint a house together \citep{Bratman:1992mi}, 
	lift a heavy sofa together \citep{Velleman:1997oo}, 
	prepare a hollandaise sauce together \citep{Searle:1990em}, 
	go to Chicago together \citep{Kutz:2000si}, 
	and walk together \citep{gilbert_walking_1990}.
In developmental psychology paradigm cases of shared agency include  two people 
	tidying up the toys together \citep{Behne:2005qh},
	cooperatively pulling handles in sequence to make a dog-puppet sing \citep{Brownell:2006gu},
	bouncing a ball on a large trampoline together \citep{Tomasello:2007gl}.

A \emph{joint action} is an action or event involving shared agency.

Shared agency raises a tangle of scientific and philosophical questions.  Psychologically we want to know which mechanisms make it possible to engage in and understand different sorts of shared agency
\citep{vesper_minimal_2010}.  
Developmentally we want to know when shared agency emerges, what it presupposes and whether abilities to engage in it somehow facilitate socio-cognitive, pragmatic or symbolic development \citep{Moll:2007gu,Hughes:2004zj,Brownell:2006gu}.  
Phenomenologically we want to characterise what (if anything) is special about experiences of action and agency when shared agency is involved \citep{Pacherie:2010fk}.  
Metaphysically we want to know what kinds of entities and structures are implied by the existence of shared agency \citep{Gilbert:1992rs,Searle:1994lb}.  
And normatively we want to know what kinds of commitments (if any) are entailed by shared agency and how these commitments arise \citep{Roth:2004ki}.
%, plus a formal account of how practical reasoning for joint action differs (if at all) from individual practical reasoning \citep{Sugden:2000mw,Gold:2007zd}

To support investigation of these questions it may be useful to have an account of shared agency that gives us a principled way of distinguishing shared from individual agency \citep[compare][]{Bratman:2009lv}.

Where could we start in constructing or evaluating an account of shared agency?
One possibility is to start with some well-known contrast cases.
Contrast cases are pairs of events which are similar in terms of the behaviour and coordination they involve but where one exemplifies shared agency  while the other does not.  
Thus \citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together involves shared agency whereas merely walking side by side is not. 
Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first is a case involves shared agency, the second does not; but the same movements occur in both.  
These sorts of contrast case invite the question, 
How does shared agency differ from individual but parallel agency? 
Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
And Searle’s example shows that the difference between shared agency and parallel individual agency can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too. 
So one constraint on any account of shared agency is that it should enable us to make systematic sense of these and other contrast cases.

\section{Shared Intention}
On the leading, best developed accounts of shared agency in philosophy and psychology, 
shared agency is explained  in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared intention.
On this widely held view, the difference between our walking together and two strangers merely walking side-by-side is that one event is appropriately related to a shared intention whereas the other is not.

Of course, explaining shared agency in terms of shared intention pushes us back to the question, What is shared intention?
The term `shared intention' is a term of art.
On many accounts, shared intentions are neither shared nor intentions.
Minimally, a shared intention stands to a joint action in roughly the way that an ordinary, individual intention stands to an ordinary, individual action.
Now an ordinary, individual intention represents an outcome, coordinates an agent's actions, and coordinates the agent's actions in such a way that, normally, this coordination would facilitate the occurrence of the represented outcome.
Similarly, a shared intention involves one or more representations of an outcome, coordinates the several agents' actions, and coordinates them in such a way that, normally, the coordination would facilitate the occurrence of the represented outcome.

Beyond this parallel there is much divergence on what shared intention is.
Some hold that it differs from
ordinary intention with respect to the attitude involved (\citealp{Searle:1990em}). 
Others have explored the notion that it differs from ordinary intention with respect to its subject, which is plural \citep{Gilbert:1992rs,helm_plural_2008}, 
or that it differs from ordinary intention in the way it arises, namely through team reasoning \citep{Gold:2007zd}, 
or that it involves distinctive obligations or commitments to others (\citealp{Gilbert:1992rs}; \citealp{Roth:2004ki}).
Opposing all such views, \citet{Bratman:1992mi,Bratman:2009lv} argues that shared intention can be realised by multiple ordinary individual intentions and other attitudes whose contents interlock in a distinctive way.

We can distinguish strong and weak claims linking shared agency to shared intention.
The weak claim is that shared intention will enable us to understand \emph{some forms} of shared agency.
This claim is neutral on whether there might be joint actions without shared intention, and on whether ingredients other than shared intention might be needed in giving a full account of shared agency.
The strong claim is that an account of shared intention gives us the whole story about shared agency, so that no other ingredients are needed.  Given this claim, for an event to be a joint action is for it to be appropriately related to a shared intention.

Some philosophers and psychologists have endorses the strong claim.  For instance:  
%
\begin{quote} 
`I take a collective action to involve a collective intention.'  \citep[p.\ 5]{Gilbert:2006wr}
\end{quote}
%
Further examples could be given  (%
	\citealp[p.\ 381]{Carpenter:2009wq}; 
	\citealp[p.\ 369]{Call:2009fk};
	\citealp{Kutz:2000si}; 
	\citealp[p.\ 117]{rakoczy_pretend_2006}; 
	\citealp{Tollefsen:2005vh}%
	).
In what follows we remain neutral on the weak claim but argue against the strong claim.
We argue against the strong claim on the grounds that shared agency is sometimes not only a matter of shared intention but may also involves structures of interlocking motor representations.
This may have consequences for some of the metaphysical, normative and phenomenological questions about shared agency mentioned above.

\section{The parallel with ordinary intentions}
Why might anyone endorse the strong claim that for an event to be a joint action is for it to be appropriately related to a shared intention? 
Those who endorse it rarely or never provide arguments.
However, two considerations might appear favour this view.

First, if someone thought that it is possible to distinguish systematically between the contrast cases by appeal to shared intention (and perhaps only by appeal to shared intention), this could motivate holding that for an event to be a joint action is for it to be appropriately related to a shared intention.
We shall argue, however, that distinguishing systematically between the contrast cases cannot be done entirely in terms of shared intention.
[*HY: this argument is missing from this draft.]

@@

Concerning this second consideration, 
we take for granted that the parallel obtains but we do not accept the view about ordinary, individual action.
Not everyone accepts that for an event to be an action is for it to be appropriately related to an intention.
Some philosophers allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Michael Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' \citet[p.\ 251]{bratman:2000_valuing}.%
%\footnote{
%For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
%describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
%}
Others reject the standard view without asserting there can be action without intention.
Instead they claim that ingredients other than intention are needed to say which events are actions.
In particular, some claim that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{pacherie:2000_content,butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.
So depending on your views about ordinary, individual intention,
the second consideration---the idea that the relation of shared intention to joint action is in some ways parallel to the relation between ordinary, individual intention and plain vanilla action---might actually support the view we aim to establish, namely that fully explaining shared agency requires appeal to structures of motor representation and not only to shared intention.
%***what's the argument for this second claim!?

\section{Motor Representation}
Since we aim to argue that a fully adequate account of shared agency must appeal to motor representation, it may be helpful first to provide some background about motor representation.

A \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.
We follow several psychologists and philosophers in supposing that motor representations feature in planning and monitoring action \citep[e.g.]{wolpert:1995internal, miall:1996_forward}.

Motor representations are in some ways similar to intentions,
as some have recently argued (\citealp[pp.\ 189-90]{pacherie:2008_action}; \citealp{butterfill:2012_intention}).
First, like intentions, some motor representations represent outcomes and not merely kinematic features of action.
Like intentions, some motor representations play a role in coordinating multiple  component activities by virtue of their role as elements in hierarchically structured plans.
And, like intentions, some motor representations coordinate these activities in a way that would normally facilitate the outcome’s occurrence.

One major dissimilarity between intentions and motor representations is that motor representations lead a kind of double life.
For motor representations are involved not only in producing actions but also in observing actions. Indeed there seem to be some striking similarities between the sorts of processes and representations usually involved in performing a particular action and those which typically occur when observing someone else perform that action \citep{rizzolatti_functional_2010,rizzolatti_mirrors_2008}.%
\footnote{ 
If motor representations occur in action observation, then observing actions might sometimes facilitate performing compatible actions and interfere with performing incompatible actions.  Both effects do indeed occur, as several studies have shown \citep{brass:2000_compatibility, craighero:2002_hand, kilner:2003_interference, costantini:2012_does}. 
}

[*HY: I'm still thinking about how best to introduce motor representation: any pointers?]

So much for the bare notion of motor representation.
Why suppose that motor representation might be needed to explain shared agency?

\section{Social motor representation}
We start from an empirical premise which is about enabling conditions for shared agency only: some joint actions are facilitated by reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent.

This needs unpacking. 
As already mentioned, a \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.
To repeat, motor representations are not concerned with merely kinematic or dynamic features of actions only.
Rather, some motor representations represent outcomes, such as the movement of a target object from one place to another.

@@

Two or more agents have \emph{reciprocal} motor representations  just if there is a single outcome and each agent has a motor representation of that outcome. 
It is hardly controversial that reciprocal motor representations exist, for their existence is suggested by by a large body of research on motor cognition in action observation.
It is more controversial that reciprocal motor representation occurs in joint action, but there is some evidence for this claim too.%
\footnote{
See \citet{kourtis:2012_predictive}: `the partner’s expected action is simulated at the motor level, which probably facilitates effective performance of the joint action.'
\citet{kourtis:2010_favoritism} show that 
reciprocal motor representation is more likely to occur in joint action than is mere observation. 
See also \citet{Knoblich:2003nf}.
 }

We want to go a tiny step further and suggest that in joint action there are sometimes reciprocal, agent-neutral representations of outcomes whose obtaining would normally involve action on the part of each of the agents.
So when we act together, some of my motor representations may concern outcomes that are partly but not entirely to be realised by my actions (and likewise for you).
For example, suppose our task is to move an object from A to B, where you pick it up and pass it to me so that I can then place it.
In this case I may represent the movement of the object from A to B and not only the component movements.
I represent a collective outcome of our actions and not just outcomes to which each of our actions are individually directed.
%
%So it is not just that, when we act together, I represent the outcomes to which your actions are directed and the outcomes to which my actions are directed; I may also represent an outcome to which all of our actions are directed.

We shall use the term \emph{social} motor representation as an abbreviation for the reciprocal, agent-neutral motor representation of outcomes whose obtaining would normally require action on the part of each reciprocating agent.
(This is probably a bad term to pick; we are still trying to come up with a better one. 
Certainly we cannot assume in advance of argument that such reciprocal, agent-neutral motor representations are social in any interesting sense;
for now we are using the term `social' in a non-standard way as an abbreviation, one that reflects our aim.)

What follows is speculative philosophy: we take for granted that  social motor representation sometimes facilitates joint action and ask whether this conjecture bears on our question about shared agency.
As a first step, we shall ask how social motor representation might facilitate joint action.
Note that answering this question does not directly commit us to any view about shared agency.
After all, social motor representation might be an enabling condition for some instances of shared agency but completely unnecessary for explaining what shared agency is.

[*HY: I'm planning a short section on evidence for social motor representation.  But as I'm going beyond the evidence anyway, I don't plan to include it in presenting this paper to philosophers.]

@@

To answer this question
let us take a step back and consider an individual action.
Suppose an agent moves a mug from one place to another, passing it from her left hand to her right hand half way.
It is a familiar idea that motor planning, like planning generally, involves starting with relatively abstract representations of outcomes and gradually filling in details.
We can capture this by supposing that 
motor representations for planning and monitoring action involve a hierarchical structure of representations.
At the top we might find a relatively abstract representation of an outcome, in this case of the movement of the object from one location to another.
Action-relevant details are progressively filled in by representations at lower stages of the hierarchy. 
Now in the action we are considering there is a need, even for the single agent, to coordinate the exchange between her two hands.
How is this achieved? 
We suppose that part of the answer involves the fact that planning for the movements of each hand is not done entirely independently.
Rather there is a plan for the whole action
and plans for the movements of each hand are components of this larger plan.
It is in part because they are parts of a larger plan that the plan for one hand constrains and is constrained by the plan for the other hand.

How is this relevant to the case of joint action?
In joint action the agents have the same goal, to move the object from one place to another.
They also face a similar coordination problem, requiring a precisely timed swap from one hand to another.
Now suppose, that the same planning is involved in the individual case (where one agent performs the whole action) and in the joint action case (where the action is distributed between two agents).
The planning is the same almost up to the actual muscle contractions.

How could this be helpful?
Suppose the agents' planning processes are similar enough that, for a given context and problem, they will produce approximately the same plans.
Then having each agent plan the whole joint action means that (i) each agent plans the other agent's action,
(ii) each agent's plan for the other agent's action is approximately the same as that agent's plan for her own action,
and 
(iii) each  agent's plans for their own action are constrained by the plans for the other agent's action.

@@

\section{Grounding the purposiveness of joint action}
So far we have only been considering a possible role for social motor representation in enabling joint action.  
How does any of this bear on our main question about shared agency?
The details of how 
social motor representation enables joint action
 already give us grounds for holding that motor representation has a role to play in explaining shared agency.

Here are two basic question about  joint action are.
%What is the relation between a purposive joint action and the outcome or outcomes to which it is directed?
What singles out the outcome or outcomes to which a purposive joint action is directed?
And what binds together the various activities (of several agents) that make up the joint action?
%A difference in the case of joint action is, of course, that the component activities are not activities of a single agent.

If we appeal to a notion of shared intention,
we can answer these questions about joint action.
A shared intention is what relates purposive joint actions to the outcomes to which they are directed.
For the shared intention 
involves a representation, on the part of each agent, of an outcome,
coordinates the several agents’ activities
and 
coordinates the several agents’ activities in such a way that would normally facilitate the occurrence of the represented outcome.
This is how a shared intention can bind together the activities comprising a joint action and link them to an outcome.
%Shared intention does for joint action roughly what ordinary intention does for ordinary, individual action.

@@

What we are suggesting is very simple.
Given the correctness of a standard view about shared intention in joint action, 
and 
given that in ordinary, individual action, motor representations  bind together activities and link them to outcomes,
it is plausible that 
in joint action, several agents' activities can be bound together and linked to an outcome by social motor representation.
That is,
the purposiveness of a joint action can be grounded not only in shared intention, but also in social motor representation.
This is why we suppose that an account of shared agency must appeal not only to shared intention but also to social motor representation.

\section{How social motor representation resembles shared intention}
It may be helpful to compare and contrast the notion of social motor representation with a notion of shared intention. 
We shall use Bratman's account of shared intention as it is the best developed. 
Here are Bratman’s collectively sufficient\footnotemark \ conditions for you and I to have a shared intention that we J:
%
\footnotetext{
In \citet{Bratman:1992mi}, the following were offered as jointly sufficient \textit{and individually necessary} conditions; the retreat to sufficient conditions occurs in \citet[][pp.\ 143-4]{Bratman:1999fr} where he notes that `for all that I have said, shared intention might be multiply realizable.'
} 
%
\begin{quote}
\label{quote:bratman_account}
`1. (a) I intend that we J and (b) you intend that we J

@@

If, as we have just argued, social motor representations play a role analogous to the structure of intentions and knowledge which Bratman identifies as sufficient for shared intention, then this is a  (non-decisive) reason to think that motor representation is also needed in characterising shared agency.
